The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
lots of todos for results

Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats, and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
stable for forest and open habitats except for a contrasting increase in
similarity for forest and decrease in similarity for open habitats 250 m
landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m there were no individuals connected in the network
layers. <!-- individuals still used forage but in much lower proportion +
lowered opportunity to associate --> Connective redundancy decreased with
increasing landcover resolution due the decrease in connectivity of individuals
in winter forage habitats, resulting in a multilayer network where neighbours
were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
time understanding this previous sentence --> (Figure\@ref(fig:lcres)d).  These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect relevant landscape features and habitats. <!-- TODO: how? This
isn't clear enough for me to follow yet -->

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below approximately 75 observations for forest, approximately
210 observations for open and approximately 300 observations for forage (Figure
\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
stabilized for all three landcover classes at approximately 200 observations for
forest and approximately 300 observations for open and forage landcover types.
Connective redundancy increased with increasing number of observations as
individuals became more connected to neighbours in multiple layers (Figure
\@ref(fig:nobs)d). Given the overall trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing the social dynamics across
contexts.

@@

Contrasting winter and summer seasons became more similar with increasing window
length. Individual graph strength and layer relevance increased for all summer
layers as individuals became more connected with increasing window lengths
(Figure \@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Layer similarity between
seasons increased consistently across landcover class (Figure
\@ref(fig:winlen)b).  These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation related to resource availability.

>>>>

Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats, and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
stable for forest and open habitats except for a contrasting increase in
similarity for forest and decrease in similarity for open habitats 250 m
landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m, there were no individuals connected in the network
layers. <!-- individuals still used forage but in much lower proportion +
lowered opportunity to associate --> Connective redundancy decreased with
increasing landcover resolution due the decrease in connectivity of individuals
in winter forage habitats, resulting in a multilayer network where neighbours
were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
time understanding this previous sentence --> (Figure\@ref(fig:lcres)d).  These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect relevant landscape features and habitats. <!-- TODO: how? This
isn't clear enough for me to follow yet -->

<!-- TODO: update this..... -->
As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below approximately 75 observations for forest, approximately
210 observations for open and approximately 300 observations for forage (Figure
\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
stabilized for all three landcover classes at approximately 200 observations for
forest and approximately 300 observations for open and forage landcover types.
Connective redundancy increased with increasing number of observations as
individuals became more connected to neighbours in multiple layers (Figure
\@ref(fig:nobs)d). Given the overall trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing the social dynamics across
contexts.

@@

<!-- TODO: update.....-->
Contrasting winter and summer seasons became more similar with increasing window
length. Individual graph strength and layer relevance increased for all summer
layers as individuals became more connected with increasing window lengths
(Figure \@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Layer similarity between
seasons increased consistently across landcover class (Figure
\@ref(fig:winlen)b).  These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation related to resource availability.
